CUNY SPS DATA 605 Final

### 2019-05-24 DATA605/MSilva_Final.Rmd
More work on final

```{r, results="asis"}
zero_vars <- c()

@@

for(variable in variables){
  d <- kaggle[,names(kaggle) == variable]
  if(is.numeric(d)){
    results <- cor.test(kaggle$SalePrice, d, conf.level = 0.8)
    if(0 > results$conf.int[1] & results$conf.int[2] > 0){
      hypothesis_test_results <- "Yes"
      zero_vars <- c(zero_vars, variable)
    } else {
      hypothesis_test_results <- "No"
    }
    cat(paste("<tr><td>",variable,"</td><td>", hypothesis_test_results, "</td>"))
  }
}
cat("</tbody></table>")
```

@@

*There are `r length(zero_vars)` variables that have no correlation with the sale price.  I would be worried be woried about family-wise error because I just ran `r length(variable)` hypothesis tests.  The family-wise error rate would be: ${FWER} = 1 - (1 - .2)^`r length(zero_vars)` = 1 - `r .8 ^ length(zero_vars)` = `r 1 - (.8^ length(zero_vars))`$.  This means there is a really high probability of committing a Type I error.*

@@

```{r}
samples <- rexp(10000, rate = lambda)
```

@@

*This analysis is available on  [https://github.com/mikeasilva/CUNY-SPS](https://github.com/mikeasilva/CUNY-SPS/blob/master/DATA605/MSilva_Final.Rmd).*

>>>>

```{r, results="asis"}
zero_vars <- 0
test <- 0

@@

for(variable in variables){
  d <- kaggle[,names(kaggle) == variable]
  if(is.numeric(d)){
    test <- test + 1
    results <- cor.test(kaggle$SalePrice, d, conf.level = 0.8)
    if(0 > results$conf.int[1] & results$conf.int[2] > 0){
      hypothesis_test_results <- "Yes"
      zero_vars <- zero_vars + 1
    } else {
      hypothesis_test_results <- "No"
    }
    cat(paste("<tr><td>",variable,"</td><td>", hypothesis_test_results, "</td>"))
  }
}
cat("</tbody></table>")
```

@@

*There are `r zero_vars` variables that have no correlation with the sale price.  I would be worried be woried about family-wise error because I just ran `r test` hypothesis tests.  The family-wise error rate would be: ${FWER} = 1 - (1 - .2)^`r zero_vars` = 1 - `r .8 ^ zero_vars` = `r 1 - (.8^ zero_vars)`$.  This means there is a really high probability of committing a Type I error.*

@@

```{r}
samples <- rexp(1000, rate = lambda)
```

@@

*This analysis is available on  [https://github.com/mikeasilva/CUNY-SPS](https://github.com/mikeasilva/CUNY-SPS/blob/master/DATA605/MSilva_Final.Rmd).  A walkthough of this analysis is available on [YouTube](https://youtu.be/W5iE-ItRvrQ).*
